---
title: "toxpi_r"
author: "Karveandhan"
date: "11/7/2022"
output: rmarkdown::github_document
---
### 1. Load Required Libraries

Load the following required libraries.

```{r setup, include=FALSE}
library(toxpiR)
library(tidyverse)
library(dplyr)
library(nycgeo)
library(rio)
library(r2r)
library(readxl)
library(hash)
library(tidycensus)
library(LaplacesDemon)
```

### 2. Create a ToxPi model using the designed toxpiheader from the process_nvi_features notebook

The topxi model can be created directly as the csv is in the format of toxpiheader. It automatically creates slices and weights for each slices as mentioned in the csv file.

```{r}
temp_model<-txpImportGui("/Users/karveandhan/Desktop/Columbia University/DASHI Project/nvi_asthma/data/processed/preprocessing/nevi_tract_features_toxpiheader.csv")
temp_model[["model"]]
```

### 3. Import the Asthma Hospitalization Data (Available in/as data/raw/AsthmaHosp_2016_lt17age.xlsx)


```{r}
asthma_hospitalization<-read_excel("/Users/karveandhan/Desktop/Columbia University/DASHI Project/nvi_asthma/data/raw/AsthmaHosp_2016_lt17age.xlsx")
asthma_hospitalization<-asthma_hospitalization[0:2266,]

#Preprocess the data and transform the Census Tract to the format of interest.
asthma_hospitalization$`Census Tract`<-asthma_hospitalization$`Census Tract`%>%
   map(function(x) gsub("[.]","",x))
asthma_hospitalization$`Census Tract`<-paste0("36",asthma_hospitalization$`Census Tract`)
asthma_hospitalization<-asthma_hospitalization%>%
  select(c('Census Tract','Total'))

```

### 4. Replace Missing Values

In the asthma hospitalization data, there are '*' that represent that there the count is less than 10 but greater than 0. So, to fill in those values we replace them with an integer between 1 to 9 generate randomly. We set a seed for reproducibility.

```{r}
set.seed(42)
asthma_hospitalization$Total<-asthma_hospitalization$Total%>%
  map(function(x) gsub("[*]",floor(runif(1, min=1, max=10)),x))
colnames(asthma_hospitalization)<-c('tract','cases')
```

### 5. Import population of under 18 for each cencus tract in New York City.

As we have the number of asthma hospitalization cases for each census tract, we now need to normalize it for each census tract based on the population in that census tract. So, we first find the population of all under18 male and female. Further, we sum both to know the population in the census tract.

```{r}
#Using the census_api_key to access the data

census_api_key('23381961ae708c9374e30013b8f40b3485999b21') 
options(tigris_use_cache = TRUE)
##### Specify county names for Census data download
county_names <- c('New York County', 'Kings County', 'Bronx County', 'Richmond County', 'Queens County')
vars <- c('B01001_027E','B01001_028E','B01001_029E','B01001_030E','B01001_003E','B01001_004E','B01001_005E','B01001_006E')
population_under18 <- get_acs(geography = "tract", state = "NY", county = county_names, variables = vars, year = 2015, survey = "acs5", output = "wide", geometry = TRUE, keep_geo_vars = TRUE) %>% 
  dplyr::as_tibble() %>% 
  dplyr::select(-geometry)


population_under18<-population_under18%>%
  transmute(tract=GEOID,female_u18=B01001_027E+B01001_028E+B01001_029E+B01001_030E,  
            #Sum of population of all age groups less than 18 (Female)
            male_u18=B01001_003E+B01001_004E+B01001_005E+B01001_006E,   #Sum of population of all age groups less than 18 (Male)
            total_u18=female_u18+male_u18)    #Sum of population of all age group less than 18 (Male+Female)



```


```{r}
nevi_preprocessed<-read_rds("/Users/karveandhan/Desktop/Columbia University/DASHI Project/nvi_asthma/data/processed/preprocessing/nevi_tract_features.rds")
asthma_hospitalization<-asthma_hospitalization%>%
  left_join(population_under18,by='tract')  #Attach the asthma hospitalization cases count with the population count.
asthma_hospitalization$cases<-as.integer(asthma_hospitalization$cases)
asthma_hospitalization<-asthma_hospitalization%>%
  filter(tract %in% nevi_preprocessed$tract)  #Remove census tract that does not exist in the pre-processed_nevi.
asthma_hospitalization<-asthma_hospitalization%>%
  mutate(asthma_ratio=cases/total_u18)        #Calculate asthma hospitalization ratio
asthma_hospitalization<-na.omit(asthma_hospitalization)     #Ignore all the data that contains missing values.
nevi_preprocessed<-nevi_preprocessed%>%
  filter(tract %in% asthma_hospitalization$tract) 
#Retain only the census tract data that does not contain any missing values of asthma hospitalization.
asthma_hospitalization<-asthma_hospitalization%>%
  mutate(asthma_ratio=asthma_ratio*1000)     #Multiply the asthma ratio by 1000 (Asthma Hospitalization per 1000 people)
```



```{r}
m=hash() #Hash map that keeps tract of all the nevi_scores and all the sub-domain scores.

best_weights=temp_model[["model"]]@txpWeights     #Copying the initial weights as the best weights. Will be replaced if a better correlation is obtained between the nevi and the asthma hospitalization count.

f.model <- TxpModel(txpSlices = temp_model[["model"]]@txpSlices, 
                    txpWeights = best_weights,
                    txpTransFuncs = temp_model[["model"]]@txpTransFuncs)

f.results <- txpCalculateScores(model = f.model, 
                                input = nevi_preprocessed,
                                id.var = 'tract' )
result_topxi<-data.frame(f.results@txpIDs)
result_topxi$nevi<-f.results@txpScores
result_topxi<-cbind(result_topxi,f.results@txpSliceScores)
asthma_data<-asthma_hospitalization%>%
  select(tract,asthma_ratio)
names(result_topxi)[names(result_topxi) == 'f.results.txpIDs']<-'tract'

result_topxi_analyse<-result_topxi%>%
  left_join(asthma_data,by='tract')%>%
  relocate(asthma_ratio, .after = nevi)
best_corr=cor(result_topxi_analyse$nevi,result_topxi_analyse$asthma_ratio,method='spearman') #Variable to keep tract of the maximum correlation achieved.

print(paste0("Baseline Correlation Achieved with equal weights :",best_corr))
```

```{r}
set.seed(42)
temp_weights<-rdirichlet(10000, rep(1,31))     
#10000 possible weights: Generate 10000 combination of 31 numbers that sum to 1. These would form the weights of the sub-domain. We further explore which of these 10000 weights produce the best correlation between the asthma hospitalization and the nevi formed.

for (i in (1:10000)){
  
f.model <- TxpModel(txpSlices = temp_model[["model"]]@txpSlices, 
                    txpWeights = temp_weights[i,],
                    txpTransFuncs = temp_model[["model"]]@txpTransFuncs)
#Develop a ToxPi model for each of the 10000 possible weight

f.results <- txpCalculateScores(model = f.model, 
                                input = nevi_preprocessed,
                                id.var = 'tract' )
# Calculate the nevi

result_topxi<-data.frame(f.results@txpIDs)
result_topxi$nevi<-f.results@txpScores
result_topxi<-cbind(result_topxi,f.results@txpSliceScores)
asthma_data<-asthma_hospitalization%>%
  select(tract,asthma_ratio)
names(result_topxi)[names(result_topxi) == 'f.results.txpIDs']<-'tract'

result_topxi_analyse<-result_topxi%>%
  left_join(asthma_data,by='tract')%>%
  relocate(asthma_ratio, .after = nevi)
current_cor=cor(result_topxi_analyse$nevi,result_topxi_analyse$asthma_ratio,method='spearman')    
#Find the correlation between the nevi and the asthma ratio

if(current_cor>best_corr) #If better result produced replace the best correlation obtained and the sub-domain weights.
{
best_corr=current_cor
best_weights=temp_weights[i,]
}
corr_weights=temp_weights[i,]
m[current_cor]=corr_weights
}
```

```{r}
print(paste("Best Correlation Acheived : ", best_corr)) 
sub_domain_name=names(result_topxi)
for (i in (1:31))
{
  print(paste(sub_domain_name[2+i],best_weights[i]))
}

```
```{r}
#Store the sub-domain weights of the best 10 correlation results produced between nevi and asthma ratio
top_10_keys=sort(keys(m),decreasing = TRUE)
top_10_keys=top_10_keys[c(1:10)]
top_10_key_value_pairs=m[top_10_keys]

corr_data=data.frame("col_name"=names(result_topxi)[3:length(result_topxi)])
corr_data['Best Value']=values(top_10_key_value_pairs[max(keys(top_10_key_value_pairs))])
for(i in keys(top_10_key_value_pairs)){
  corr_data[paste('Corr_Val',i)]=values(top_10_key_value_pairs[i])
}

```

Temperory workspace document:
1. Plots (Distribution of Green space data, water and air pollution data)
2. Linear Model Analysis
3. Clustering Analysis
4. Correlation Analysis

Things to try out:
Gradient descent way of optimizing the sub-domain scores to attain a good correlation between the nevi index and the asthma hospitalization data